Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1123 at $z$=0.654

### 2016-05-17 WRITEUP/ms.tex
done with CO21 high-order moments section

\subsection{\bco kinematics}
\begin{figure}[!htbp]
\centering
\includegraphics[trim=0 5 0 15, clip, width=0.25\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}
\includegraphics[trim=0 5 0 15, clip, width=0.25\textwidth]{../Figures/F555W_REDBLUE.eps}
\includegraphics[width=0.5\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
\caption{
Contours for the first (left) and second (right) moment maps are shown in steps of 50 \kms, and 100 \kms, respectively. The beam (native resolution) is shown in the right panel.
\label{fig:CO21highO}}
\end{figure}

A clear velocity gradient

An unusually high velocity dispersion ($\gtrsim$400\kms) is seen in the
central region in \Fig{CO21highO}. While beam smearing is inevitably the
dominant factor giving rise to the observed velocity dispersion
at current spatial resolution, the exceedingly high velocity dispersion hints
at potential perturbations from the AGN, or internal turbulence due to
interactions with the companion, and/or instability due to the huge gas
reservoir.

Given the 1st moment map and the observed velocity gradient across the source plane in our model \Fig{model}, this is indicative of a kinematically ordered galaxy, but its emission has been lensed differentially.

and velocity dispersion are suggestive of a kinematically ordered disk at the current resolution limit. The spectrally resolved lensed emission allows us to probe dynamical structures on smaller spatial scales than otherwise possible.

We will defer the discussion of such features and the implications to
\Sec{dynamics}, where we analyze the dynamics of the system.

@@

%--------------------------------------------------------------------------
%                                Analysis
%--------------------------------------------------------------------------
\section{Analysis}
\subsection{Lens modeling} \label{lensmodel}
With the high SNR and spectral resolution, we model different kinematic components using our lensing code \uvmcmcfit.

>>>>

\subsection{\bco kinematics} % DONE
A clear velocity gradient and an unusually high
velocity dispersion ($\gtrsim$400\kms) near the central region
is seen in \Fig{CO21highO}. While beam smearing is inevitably the
dominant factor in the observed velocity dispersion
at the spatial resolution of this data, the exceedingly
high velocity dispersion hints
at potential perturbations from the AGN, or internal turbulence due to
interactions with the companion, and/or instability due to the large gas
content. A velocity gradient across the source plane in \Fig{model} is also
found in our lens model. This further supports the idea of a kinematically-
ordered galaxy, but its emission has been lensed differentially.
In this scenario, RXJ1131 is a disrupted disk galaxy hosting an optically
bright quasar and is in the process of merging.
We will defer the discussion of the implications to \Sec{dynamics},
where we analyze the dynamics of the system in the source plane.

\begin{figure}[!htbp]
\centering
\includegraphics[trim=0 5 0 15, clip, width=0.25\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}
\includegraphics[trim=0 5 0 15, clip, width=0.25\textwidth]{../Figures/F555W_REDBLUE.eps}
\includegraphics[width=0.5\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
\caption{
Contours for the first (left) and second (right) moment maps are shown in steps of 50 \kms, and 100 \kms, respectively. The beam (native resolution) is shown in the right panel.
\label{fig:CO21highO}}
\end{figure}

@@

%--------------------------------------------------------------------------
%                                Analysis
%--------------------------------------------------------------------------
\section{Analysis}
\subsection{Lens modeling} \label{lensmodel}
The spectrally resolved lensed emission allows us to probe dynamical structures on smaller spatial scales than otherwise possible.

With the high SNR and spectral resolution, we model different kinematic components using our lensing code \uvmcmcfit.
